Open-source tools in R for landscape ecology

### 2021-01-26 paper/paper.Rmd
added gdal, proj, epsg and simple features to glossary

API & Application programming interface. A set of protocols for sending and retrieving information from a server \\
cell & Smallest, rectangular unit of raster data model \\
CRAN & Comprehensive R Archive Network. A repository for R packages \\
CRS & Coordinate references systems. A coordinate-based local, regional or global system used to locate geographical entities \\
GIS & Geographical information system \\
landscape & Mosaic of land covers, ecosystems, habitat types, land uses \\
NLM & Neutral landscape model \\
open-source software & Software released under licenses that allow to use, modify and distribute it \\
patch & Neighboring cells with same value \\
raster & Cell grid based data model \\
resolution & Size in meter or degree of one cell \\
R package & User-created software extension to R programming language \\
SDM & Species distribution modelling \\
vector & Points, lines, and polygons-based data model \\

>>>>

API & Application programming interface. A set of protocols for sending and retrieving information from a server \\
cell & Smallest, rectangular unit of raster data model \\
CRAN & Comprehensive R Archive Network. A repository for R packages \\
CRS & Coordinate references systems. A coordinate-based local, regional or global system used to locate geographical entities \\
EPSG & Public registry of geodetic datums, spatial reference systems, Earth ellipsoids, coordinate transformations and related units of measurement \\
GDAL & Open source translator library for raster and vector geospatial data formats \\
GIS & Geographical information system \\
landscape & Mosaic of land covers, ecosystems, habitat types, land uses \\
NLM & Neutral landscape model \\
open-source software & Software released under licenses that allow to use, modify and distribute it \\
patch & Neighboring cells with same value \\
PROJ & Open source generic coordinate transformation software \\
raster & Cell grid based data model \\
resolution & Size in meter or degree of one cell \\
R package & User-created software extension to R programming language \\
SDM & Species distribution modelling \\
Simple Features & A set of standards that specify a common storage and access model of geographic features \\
vector & Points, lines, and polygons-based data model \\
